%*******************************************************
% Acknowledgments
%*******************************************************

\addcontentsline{toc}{chapter}{Acknowledgments}
\chapter*{Acknowledgments}

I would like to take this opportunity to thank some people who helped me do the research.

I would like to thank my supervisor Dr. Tu Yanjun for giving me the opportunity to do the research, for her support on my research and for her guidance and suggestions on my analysis.

I would like to thank Dr. Zhang Dongliang.
He taught me almost everything on the analysis.
He helped me get familiar with the linux software: the linux shell, the text editor (vim) and the revision control system (svn).
He taught me how to use the ATLAS software: the event analysis software (ROOT and RootCore), the data acquisition software(dq2 and rucio) and the distributed computing management (grid and panda).
I learnt the typesetting system (latex) from him.
He taught me the ALTAS detector: trigger system and GRL.
He also helped our group write the multiLepSearch package to generate the ntuple.

I would like to thank Dr. Daniela Katherinne Paredes Hernandez.
She gave a lot of suggestions on my analysis.
She designed the validation region and helped me do the analysis.

I would like to thank Dr. Jeanette Miriam Lorenz from Ludwig Maximilian University of Munich.
She wrote the package HistFitter and its configuration file for our analysis.
She also organized different taskes for our group.

I would like to thank Peter Tornambe from Albert Ludwig University of Freiburg.
He estimated the fake lepton background.
He helped me generate the ntuple and cross check with his results for the yields of different processes and the fake lepton background.

I would like to thank Daniela Maria Kock from Ludwig Maximilian University of Munich.
She produced the official ntuple for our analysis, with the systematic uncertainties.
These ntuples are very helpful to cross check the yields of different processes.
She also helped me choose the list of MC samples used in our analysis.

All the plots and tables I show here are made by me, except the plots in chapter \ref{ch:VR} and the N-1 plots in chapter \ref{ch:result}.
The study of the systematic uncertainties is not done by me, therefore it is not included here.
The following are my contributions to the public paper \cite{Wh} \cite{WhSS}.
\begin{enumerate}
\item An alternative method for the SR optimization are used as a cross-check for the signal regions optimized by Daniela Maria Kock. I also suggested that she can use $m_{T2}$ for optimization.
\item I contribute to the ntuple production for the charge flip background used by Gabriel Gallardo. I also maintain the framework of the charge flip estimation.
\item I provide the cross-check to the work by Peter Tornambe (fake lepton background) and Daniela Paredes (validation region).
\end{enumerate}
