%************************************************
\chapter{This is chapter one}
\label{ch:name4}
%************************************************
\section{Introduction}
\label{sec:ch_4_introduction}

\citet{Berg2016} argues that this is a topic sentence followed by explanation, elaboration and examples to introduce the next three subsections. The last sentence of this paragraph shall introduce the next paragraph.

This is a topic sentence followed by explanation, elaboration and examples to introduce the next three subsections \citep{Collins2016}. The last sentence of this paragraph shall introduce the next paragraph.

\citet{Graham2016} and \citet{Grant2016} assert that this is a topic sentence followed by explanation, elaboration and examples to introduce the next three subsections. The last sentence of this paragraph shall introduce the next paragraph.

\section{First main stuff}
\label{sec:ch_4_firstmain}

This is a topic sentence followed by explanation, elaboration and examples to introduce this paragraph \citep{Haney2016}. The last sentence of this paragraph shall introduce the next paragraph.

This is a topic sentence followed by explanation, elaboration and examples to introduce this paragraph \citep{Jordan2016,Morgan2016}. The last sentence of this paragraph shall introduce the next paragraph.

This is a topic sentence followed by explanation, elaboration and examples to introduce this paragraph. The last sentence of this paragraph shall introduce the next paragraph.

\section{Second main stuff}
\label{sec:ch_4_secondmain}

This is a topic sentence followed by explanation, elaboration and examples to introduce this paragraph \citep{Scott2016}. The last sentence of this paragraph shall introduce the next paragraph.
 
As \citet{Wells2016} and \citet{Williamson2016}.
This is a topic sentence followed by explanation, elaboration and examples to introduce this paragraph \citep{Stewart2016}. The last sentence of this paragraph shall introduce the next paragraph.

This is a topic sentence followed by explanation, elaboration and examples to introduce this paragraph \citep{Gallagher2016}. The last sentence of this paragraph shall introduce the next paragraph.
